WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-17 paper/Manuscript.Rmd
add middle initials
sorry I forgot this before!
fix urls

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    affiliation: "3,4"
  - name: "Loek Brinkman"
    affiliation: "2,5"
  - name: "Anna-Lena Lamprecht"
    affiliation: "2,6"
    email: "a.l.lamprecht@uu.nl"
  - name: "Aaron Peikert"
    affiliation: "3,7"
  - name: "Marijn E. Struiksma"
    affiliation: "2,8"
  - name: "Barbara Vreede"
    affiliation: "9"

@@

Lindsay and colleagues [-@lindsayResearchPreregistration1012016] define
preregistration as "creating a permanent record of your study plans before you
look at the data. The plan is stored in a date-stamped, uneditable file in a
secure online archive." Two such archives are well-known in the social sciences:
[AsPredicted.org](https://aspredicted.org/), and [OSF.io](https://osf.io/).
However, 'Git' cloud hosting services also conform to these standards.
Thus, it is possible to preregister a study simply by committing a preregistration document
to the local 'Git' repository, and pushing it to the remote repository.
Subsequently [taging the release](https://help.github.com/en/github/administering-a-repository/creating-releases)
as "Preregistration" on the remote repository renders it distinct from all other commits,
and easily findable by people and programs.
This approach is simple, quick, and robust.
Moreover, it is compatible with formal preregistration through services
such as AsPredicted.org or OSF.io:
If the preregistration is
written using dynamic document generation, as 
recommended in WORCS, this file can be rendered to PDF and uploaded as an attachment
to the formal preregistration service.

@@

The `worcs` workflow facilitates preregistration,
primarily by explicitly inviting a user to write the preregistration document.
To this end, `worcs` imports several preregistration templates from the R package
`prereg` [@austPreregMarkdownTemplates2019], including templates from
organizations like [AsPredicted.org](AsPredicted.org) and [OSF.io](OSF.io), and
from researchers [e.g., @vantveerPreregistrationSocialPsychology2016].
When initializing an RStudio project with the `worcs` project template, one of
these preregistration templates can be selected, which will generate a file
called `preregistration.Rmd`. This file should be used to document study plans,
ideally prior to data collection. 
Within the workflow, the 'Git' cloud hosting services can be used to preregister a study simply by pushing a text document with the study plans to a 'Git' remote repository.
By [tagging the commit](https://help.github.com/en/github/administering-a-repository/creating-releases) as a preregistration
(see [the workflow vignette](https://cjvanlissa.github.io/worcs/articles/setup.html)),
it is distinct from all other commits, and easily findable by people and machines.

>>>>

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    affiliation: "3,4"
  - name: "Loek Brinkman"
    affiliation: "2,5"
  - name: "Anna-Lena Lamprecht"
    affiliation: "2,6"
    email: "a.l.lamprecht@uu.nl"
  - name: "Aaron Peikert"
    affiliation: "3,7"
  - name: "Marijn E. Struiksma"
    affiliation: "2,8"
  - name: "Barbara M.I. Vreede"
    affiliation: "9"

@@

Lindsay and colleagues [-@lindsayResearchPreregistration1012016] define
preregistration as "creating a permanent record of your study plans before you
look at the data. The plan is stored in a date-stamped, uneditable file in a
secure online archive." Two such archives are well-known in the social sciences:
[AsPredicted.org](https://aspredicted.org/), and [OSF.io](https://osf.io/).
However, 'Git' cloud hosting services also conform to these standards.
Thus, it is possible to preregister a study simply by committing a preregistration document
to the local 'Git' repository, and pushing it to the remote repository.
Subsequently [taging the release](https://docs.github.com/en/free-pro-team@latest/github/administering-a-repository/managing-releases-in-a-repository)
as "Preregistration" on the remote repository renders it distinct from all other commits,
and easily findable by people and programs.
This approach is simple, quick, and robust.
Moreover, it is compatible with formal preregistration through services
such as AsPredicted.org or OSF.io:
If the preregistration is
written using dynamic document generation, as 
recommended in WORCS, this file can be rendered to PDF and uploaded as an attachment
to the formal preregistration service.

@@

The `worcs` workflow facilitates preregistration,
primarily by explicitly inviting a user to write the preregistration document.
To this end, `worcs` imports several preregistration templates from the R package
`prereg` [@austPreregMarkdownTemplates2019], including templates from
organizations like [AsPredicted.org](AsPredicted.org) and [OSF.io](OSF.io), and
from researchers [e.g., @vantveerPreregistrationSocialPsychology2016].
When initializing an RStudio project with the `worcs` project template, one of
these preregistration templates can be selected, which will generate a file
called `preregistration.Rmd`. This file should be used to document study plans,
ideally prior to data collection. 
Within the workflow, the 'Git' cloud hosting services can be used to preregister a study simply by pushing a text document with the study plans to a 'Git' remote repository.
By [tagging the commit as a release](https://docs.github.com/en/free-pro-team@latest/github/administering-a-repository/managing-releases-in-a-repository), labelled "preregistration"
(see [the workflow vignette](https://cjvanlissa.github.io/worcs/articles/setup.html)),
it is distinct from all other commits, and easily findable by people and machines.

### 2020-11-17 paper/Manuscript_DS.Rmd
fix urls

The functionality of Git is enhanced by services such as GitHub
(https://github.com). GitHub is best understood as a cloud storage service
with social networking functionality. The cloud storage aspect
of GitHub allows you to "clone" (copy) a local Git repository to
the GitHub website, as a backup or research archive.
The GitHub platform offers additional functionality over Git. 
One such feature is that specific stages in the lifecycle of a project
can be [tagged as a "release"](https://help.github.com/en/github/administering-a-repository/creating-releases):
A named downloadable snapshot of a specific state of the project,
that is prominently featured on the GitHub project page.
The WORCS procedure encourages users to create releases to demarcate project milestones
such as preregistration and submission to a journal.
Releases are also useful to mark the submission of a revised manuscript, and publication.

@@

Lindsay and colleagues [-@lindsayResearchPreregistration1012016] define
preregistration as "creating a permanent record of your study plans before you
look at the data. The plan is stored in a date-stamped, uneditable file in a
secure online archive." Two such archives are well-known in the social sciences:
[AsPredicted.org](https://aspredicted.org/), and [OSF.io](https://osf.io/).
However, Git cloud hosting services also conform to these standards.
Thus, it is possible to preregister a study simply by committing a preregistration document
to the local Git repository, and pushing it to the remote repository.
Subsequently [taging the release](https://help.github.com/en/github/administering-a-repository/creating-releases)
as "Preregistration" on the remote repository renders it distinct from all other commits,
and easily findable by people and programs.
This approach is simple, quick, and robust.
Moreover, it is compatible with formal preregistration through services
such as AsPredicted.org or OSF.io:
If the preregistration is
written using dynamic document generation, as 
recommended in WORCS, this file can be rendered to PDF and uploaded as an attachment
to the formal preregistration service.

@@

The `worcs` workflow facilitates preregistration,
primarily by explicitly inviting a user to write the preregistration document.
To this end, `worcs` imports several preregistration templates from the `R` package
`prereg` [@austPreregMarkdownTemplates2019], including templates from
organizations like [AsPredicted.org](AsPredicted.org) and [OSF.io](OSF.io), and
from researchers [e.g., @vantveerPreregistrationSocialPsychology2016].
When initializing an RStudio project with the `worcs` project template, one of
these preregistration templates can be selected, which will generate a file
called `preregistration.Rmd`. This file should be used to document study plans,
ideally prior to data collection. 
Within the workflow, the Git cloud hosting services can be used to preregister a study simply by pushing a text document with the study plans to a Git remote repository.
By [tagging the commit](https://help.github.com/en/github/administering-a-repository/creating-releases) as a preregistration
(see [the workflow vignette](https://cjvanlissa.github.io/worcs/articles/workflow.html)),
it is distinct from all other commits, and easily findable by people and machines.

>>>>

The functionality of Git is enhanced by services such as GitHub
(https://github.com). GitHub is best understood as a cloud storage service
with social networking functionality. The cloud storage aspect
of GitHub allows you to "clone" (copy) a local Git repository to
the GitHub website, as a backup or research archive.
The GitHub platform offers additional functionality over Git. 
One such feature is that specific stages in the lifecycle of a project
can be [tagged as a "release"](https://docs.github.com/en/free-pro-team@latest/github/administering-a-repository/managing-releases-in-a-repository):
A named downloadable snapshot of a specific state of the project,
that is prominently featured on the GitHub project page.
The WORCS procedure encourages users to create releases to demarcate project milestones
such as preregistration and submission to a journal.
Releases are also useful to mark the submission of a revised manuscript, and publication.

@@

Lindsay and colleagues [-@lindsayResearchPreregistration1012016] define
preregistration as "creating a permanent record of your study plans before you
look at the data. The plan is stored in a date-stamped, uneditable file in a
secure online archive." Two such archives are well-known in the social sciences:
[AsPredicted.org](https://aspredicted.org/), and [OSF.io](https://osf.io/).
However, Git cloud hosting services also conform to these standards.
Thus, it is possible to preregister a study simply by committing a preregistration document
to the local Git repository, and pushing it to the remote repository.
Subsequently [taging the release](https://docs.github.com/en/free-pro-team@latest/github/administering-a-repository/managing-releases-in-a-repository)
as "Preregistration" on the remote repository renders it distinct from all other commits,
and easily findable by people and programs.
This approach is simple, quick, and robust.
Moreover, it is compatible with formal preregistration through services
such as AsPredicted.org or OSF.io:
If the preregistration is
written using dynamic document generation, as 
recommended in WORCS, this file can be rendered to PDF and uploaded as an attachment
to the formal preregistration service.

@@

The `worcs` workflow facilitates preregistration,
primarily by explicitly inviting a user to write the preregistration document.
To this end, `worcs` imports several preregistration templates from the `R` package
`prereg` [@austPreregMarkdownTemplates2019], including templates from
organizations like [AsPredicted.org](AsPredicted.org) and [OSF.io](OSF.io), and
from researchers [e.g., @vantveerPreregistrationSocialPsychology2016].
When initializing an RStudio project with the `worcs` project template, one of
these preregistration templates can be selected, which will generate a file
called `preregistration.Rmd`. This file should be used to document study plans,
ideally prior to data collection. 
Within the workflow, the Git cloud hosting services can be used to preregister a study simply by pushing a text document with the study plans to a Git remote repository.
By [tagging the commit](https://docs.github.com/en/free-pro-team@latest/github/administering-a-repository/managing-releases-in-a-repository) as a preregistration
(see [the workflow vignette](https://cjvanlissa.github.io/worcs/articles/workflow.html)),
it is distinct from all other commits, and easily findable by people and machines.

### 2020-11-17 paper/reviews_ds.Rmd
fix urls

> The GitHub platform offers additional functionality over Git. 
One such feature is that specific stages in the lifecycle of a project
can be [tagged as a "release"](https://help.github.com/en/github/administering-a-repository/creating-releases):
A named downloadable snapshot of a specific state of the project,
that is prominently featured on the GitHub project page.
The WORCS procedure encourages users to create releases to demarcate project milestones
such as preregistration and submission to a journal.
Releases are also useful to mark the submission of a revised manuscript, and publication.

>>>>

> The GitHub platform offers additional functionality over Git. 
One such feature is that specific stages in the lifecycle of a project
can be [tagged as a "release"](https://docs.github.com/en/free-pro-team@latest/github/administering-a-repository/managing-releases-in-a-repository):
A named downloadable snapshot of a specific state of the project,
that is prominently featured on the GitHub project page.
The WORCS procedure encourages users to create releases to demarcate project milestones
such as preregistration and submission to a journal.
Releases are also useful to mark the submission of a revised manuscript, and publication.
